\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{User Manual and README}
\author{Project Team}
\date{May 2025}

\begin{document}

\maketitle

\section{Jira Project Link}
You can track project progress, issues, and tasks using the Jira board at the following link:
\begin{verbatim}
https://cs3338-group3.atlassian.net/jira/software/projects/FP/boards/36
\end{verbatim}

\section{Formal Objective Breakdown}
The software system has been designed to provide users with a safe and data-informed navigation experience. Its key objectives are:
\begin{itemize}
    \item To help achieve Vision Zero's goal of reducing traffic fatalities and severe injuries to zero.
    \item To visualize data on a dynamic map interface for better understanding of traffic conditions.
    \item To integrate and utilize both historical and real-time data for improved decision-making.
    \item To assist users in planning and completing their journeys safely.
\end{itemize}



\section{Goals and Reason Why It Is Needed}
The application addresses a critical need for safer urban mobility. With increasing traffic density and safety concerns, there is a growing demand for solutions that:
\begin{itemize}
    \item Provide clear, data-driven insights into traffic patterns.
    \item Help municipalities and individuals make informed decisions to avoid high-risk areas.
    \item Contribute to broader safety initiatives like Vision Zero by reducing the chances of accidents.
    \item Enhance the overall commuting experience through real-time guidance and alerts.
\end{itemize}


\section{How to Download or Access}
To access the application, simply clone the repository from GitHub:
\begin{verbatim}
https://github.com/LMorales41/assignment-4.git
\end{verbatim}


\section{Additional Information}
For detailed system requirements and design, refer to the provided SRS (Software Requirements Specification) and SDD (Software Design Document) included in the repository. These documents cover the technical architecture, detailed requirements, and design strategies employed.

\end{document}
